Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-30 03_experiments/experiments.tex
Add fab correction
Correct one parameter for Tofts in the results
Add link to zenodo

The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
The data used for this work are also publicly available\footnote{\url{http://kaggle.com}}.

@@

\begin{equation}
  R^2 = 1 - \frac{\sum_{t = 0}^{T} (s_t - \hat{s}_t)^2}{\sum_{t = 0}^{T} (s_t - \bar{s})^2} ,
  \label{eq:r2}
\end{equation}

@@

Mean and standard-deviation of the coefficient of determination $R^{2}$ is reported in Table~\ref{tab:r2} for each quantification model.
Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.%, implying that they are adequate models for that purpose.
Additionally, the proposed \ac{pun} model does not seem to fit well the data.
Normalizing the data improve the coefficient $R^2$ for all the methods apart of the Hoffmann model.
The large standard deviation for this model might imply that there is some cases, that the fitting fails.

@@

\begin{table*}
  \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{rf} classifier.}
  \centering
  \resizebox{\columnwidth}{!}{
  \begin{tabular}{l c c}
    \toprule
    \textbf{Features} & Un-normalized data & Normalized data \\
    \midrule
    \textbf{Brix model} & & \\
    \quad $A$         & 0.54 & 0.55 \\
    \quad $k_{el}$    & 0.51 & 0.50 \\
    \quad $k_{ep}$    & 0.55 & 0.58 \\
    \textbf{Hoffmann model} & & \\
    \quad $A$         & 0.52 & 0.51 \\
    \quad $k_{el}$    & 0.55 & 0.53 \\
    \quad $k_{ep}$    & 0.55 & 0.54 \\
    \textbf{Tofts model with population \ac{aif}} & & \\
    \quad $K_{trans}$ & 0.56 & 0.55 \\
    \quad $v_{e}$     & 0.49 & 0.49 \\
    \quad $v_{p}$     & 0.53 & 0.50 \\
    \textbf{Tofts model with patient \ac{aif}} & & \\
    \quad $K_{trans}$ & 0.57 & 0.57 \\
    \quad $v_{e}$     & 0.51 & 0.53 \\
    \quad $v_{p}$     & 0.53 & 0.55 \\
    \textbf{\ac{pun} model} & & \\
    \quad $a_0$       & 0.52 & 0.53 \\
    \quad $r$         & 0.55 & 0.57 \\
    \quad $\beta$     & 0.53 & 0.55 \\
    \textbf{Semi-quantitative analysis} & & \\
    \quad wash-in     & 0.57 & 0.53 \\
    \quad wash-out    & 0.52 & 0.49 \\
    \quad IAUC        & 0.51 & 0.51 \\
    \quad $\tau$      & 0.57 & 0.54 \\
    \quad $S_M - S_0$ & 0.56 & 0.53 \\
    \bottomrule
  \end{tabular}
  }
  \label{tab:resfeats}
\end{table*}

>>>>

The implementation of the registration (C++), normalization (Python), and classification pipeline (Python) are publicly available on GitHub\footnote{\url{https://github.com/I2Cvb/lemaitre-2016-nov/tree/master}}.
The data used for this work are also publicly available\footnote{\url{https://zenodo.org/record/61163}}.

@@

\begin{equation}
  R^2 = 1 - \frac{\sum_{t = 1}^{T} (s_t - \hat{s}_t)^2}{\sum_{t = 1}^{T} (s_t - \bar{s})^2} ,
  \label{eq:r2}
\end{equation}

@@

Mean and standard-deviation of the coefficient of determination $R^{2}$ is reported in Table~\ref{tab:r2} for each quantification model.
Brix, Hoffmann, and Tofts models are fitted with a coefficient $R^{2}$ superior to 0.80.
Additionally, the proposed \ac{pun} model does not seem to fit well the data.
Normalizing the data improve the coefficient $R^2$ for all the methods apart of the Hoffmann model.
The large standard deviation for this model might imply that there is some cases, that the fitting fails.

@@

\begin{table*}
  \caption{\acs*{auc} for each individual pharmacokinetic parameter using a \acs*{rf} classifier.}
  \centering
  \resizebox{\columnwidth}{!}{
  \begin{tabular}{l c c}
    \toprule
    \textbf{Features} & Un-normalized data & Normalized data \\
    \midrule
    \textbf{Brix model} & & \\
    \quad $A$         & 0.54 & 0.55 \\
    \quad $k_{el}$    & 0.51 & 0.50 \\
    \quad $k_{ep}$    & 0.55 & 0.58 \\
    \textbf{Hoffmann model} & & \\
    \quad $A$         & 0.52 & 0.51 \\
    \quad $k_{el}$    & 0.55 & 0.53 \\
    \quad $k_{ep}$    & 0.55 & 0.54 \\
    \textbf{Tofts model with population \ac{aif}} & & \\
    \quad $K_{trans}$ & 0.56 & 0.55 \\
    \quad $k_{ep}$     & 0.49 & 0.49 \\
    \quad $v_{p}$     & 0.53 & 0.50 \\
    \textbf{Tofts model with patient \ac{aif}} & & \\
    \quad $K_{trans}$ & 0.57 & 0.57 \\
    \quad $k_{ep}$     & 0.51 & 0.53 \\
    \quad $v_{p}$     & 0.53 & 0.55 \\
    \textbf{\ac{pun} model} & & \\
    \quad $a_0$       & 0.52 & 0.53 \\
    \quad $r$         & 0.55 & 0.57 \\
    \quad $\beta$     & 0.53 & 0.55 \\
    \textbf{Semi-quantitative analysis} & & \\
    \quad wash-in     & 0.57 & 0.53 \\
    \quad wash-out    & 0.52 & 0.49 \\
    \quad IAUC        & 0.51 & 0.51 \\
    \quad $\tau$      & 0.57 & 0.54 \\
    \quad $S_M - S_0$ & 0.56 & 0.53 \\
    \bottomrule
  \end{tabular}
  }
  \label{tab:resfeats}
\end{table*}
